The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-10-04 manuscript.Rmd
refactor abstract

Museum collections have been recording our knowledge about species and their geographic ranges for about 250 years, but until recently, this information was fragmented across institutions and difficult to synthesize. The digitization of natural history collections and other biodiversity information systems can now be used to enable synthesis and highlight knowledge gaps. Here we use these data to synthesize the state of our knowledge for marine invertebrates in the continental United States. We show that current knowledge and sampling efforts are inadequate given the diversity of the fauna and the geographic extent of US. While recent high-throughput sequencing technologies promise to greatly speed up the documentation of marine species and their ranges, its value will be greatly improved by anchoring the results into existing DNA sequence data and associated vouchers. However, the best documented phyla have at most 25% of their species sequenced for even the most widely used DNA barcoding gene, cytochrome oxidase I (COI). More sampling, coordinated at the national scale, is needed to improve our knowledge of species and their geographic ranges. This data is needed to detect the impact of climate change and other anthropogenic strains to the environment. Advances in computing, information systems, and sequencing technologies, have set the stage to inform where future efforts for documenting biodiversity should be applied.

>>>>

Museum collections have been recording our knowledge about species and their geographic ranges for about 250 years, but until recently, this information was fragmented across institutions and difficult to synthesize. The digitization of biodiversity information is now enabling the synthesis of this information and can be used to highlight knowledge gaps. Here we use publicly accessible biodiversity data to assemble a list of `r format(n_distinct(combined_species$worms_valid_name), big.mark = ",")` species of marine invertebrates from the continental United States. The extent of our knowledge about species richness is limited by sampling effort. While recent developments in high-throughput sequencing promise to greatly speed up the documentation of marine species and their ranges, its value will be improved by anchoring the results into existing DNA sequence data and associated vouchers. However, the best documented phyla have at most 25% of their species sequenced for even the most widely used DNA barcoding gene, cytochrome oxidase I (COI), but for many species these records have been sampled in other biogeographic areas. More sampling, coordinated at the national scale, is needed to improve our knowledge of species and their geographic ranges. This data is needed to detect the impact of climate change and other anthropogenic strains to the environment. Advances in computing, information systems, and sequencing technologies, have set the stage to inform where future efforts for documenting biodiversity should be applied.
